%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Jennifer Manguiat} \\ \vspace{1pt}
    \small 513-519-6618 $|$ \href{mailto:jennmanguiat@gmail.com}{\underline{jennmanguiat@gmail.com}} $|$ \href{https://www.linkedin.com/in/jennifer-manguiat-42455613}{\underline{LinkedIn}} 
    %$|$
    %\href{https://github.com/andrewmanguiat}
    %{\underline{GitHub}}
\end{center}

%-----------EXPERIENCE-----------
\section{HR Leadership Skills Summary}
    \resumeItemListStart
        \resumeItem{Collaborate with executive leadership, business segment leaders and managers to strategize and execute organizational processes covering compensation and analysis, engagement, and succession/leadership planning.}
        \resumeItem{Strategic Advisor providing comprehensive guidance and support to cross-functional teams including Sales, Customer Success, Product Development and Product Management, ensuring alignment of HR strategies with overarching business objectives.}
        \resumeItem{Lead a team of a Business Partner, HR Operations Team Lead, and HR Operations Specialist, fostering their professional growth while effectively managing day-to-day HR operations.}
        \resumeItem{Implement strategic policies and processes aligned with organizational values, resulting in enhanced employee engagement and alignment with company objectives.}
        \resumeItem{Provide expert counsel and cultivate strong relationships with leaders to address employee relations matters, spanning performance management, disciplinary actions, terminations, conflict resolution and interpretation of policy and procedures.}
        \resumeItem{Lead the investigation and resolution of employee concerns and grievances, working in collaboration with legal counsel as needed.}
        \resumeItem{Champion company culture by implementing impactful and innovative policies, benefits, Gallup Q12 tools, and engagement initiatives designed to elevate employee participation and commitment.}
        \resumeItem{Collaborate with the talent acquisition team to analyze turnover trends, provide guidance on current compensation trends, and contribute to the selection of top talent.}
        \resumeItem{Oversee the administration of benefits, encompassing the FMLA/leave process, ADA accommodations, FLSA compliance, benefits communications, and open enrollment. Additionally, possess experience in collaborating with benefits brokers for annual benefits review and selection processes.}
        \resumeItem{Oversee the comprehensive reporting of engagement metrics to the executive leadership.}
        \resumeItem{Collaborate with executive leadership, legal counsel and business segment leaders to plan and execute reorganizations and reductions in force.}
        \resumeItem{In collaboration with the Chief People Officer, lead the successful onboarding and culture integration of employees from nine companies over a seven- year period through mergers and acquisitions.}
        \resumeItem{Collaborate with executive leadership, M\&A team, and legal counsel in due diligence and project management processes for mergers and acquisitions, encompassing communication and change management planning and execution.}
        \resumeItem{Led HR project initiatives within the M\&A team, overseeing the planning and execution of a 200-employee acquisition in 2022.}
    \resumeItemListEnd

\section {Recent Experience}
    \resumeSubHeadingListStart
        \resumeSubheading 
            {{People \& Culture Director}  \emph{\small\textmd{}}}{2017 -- Present} {ConstructConnect } {Cincinnati, OH}
            \resumeItem{Integral member of the HR Leadership Team at a prominent software provider specializing in preconstruction solutions, overseeing operations for approximately 800 employees across the US and Canada.}
         \resumeSubheading 
            {{HR Manager}  \emph{\small\textmd{}}}{2013 -- 2017} {ConstructConnect} {Cincinnati, OH}  
         \resumeSubheading 
            {{HR Generalist}  \emph{\small\textmd{}}}{2007 -- 2013} {ConstructConnect} {Cincinnati, OH}  
        \resumeSubheading 
            {{HR Generalist}  \emph{\small\textmd{}}}{1998 -- 2007} {Hills Communities} {Cincinnati, OH}
            \resumeItem{Key contributor within the Corporate HR team of a multi-state homebuilder and property
management company.}
    \resumeSubHeadingListEnd

\section{Education \& Certification}
    \resumeSubHeadingListStart
        \resumeSubheading{Master of Arts in Human Resources}{University of Cincinnati}{}{}
        \resumeSubheading{Bachelor of Since in HR \& Business Management}{Franklin University}{}{}
        \resumeSubheading{SPHR}{Senior Professional in Human Resources Certification}{}{}
    \resumeSubHeadingListEnd

\end{document}
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------