%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Drew Manguiat} \\ \vspace{1pt}
    \small 513-504-0277 $|$ \href{mailto:dwmanguiat@gmail.com}{\underline{dwmanguiat@gmail.com}} $|$ \href{https://www.linkedin.com/in/andrewmanguiat/}{\underline{LinkedIn}} 
    %$|$
    %\href{https://github.com/andrewmanguiat}
    %{\underline{GitHub}}
\end{center}

%-----------EXPERIENCE-----------
\section{Recent Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {{Senior Data Engineer} $|$ \emph{\small\textmd{Snowflake, AWS, Python, Apache Airflow, FiveTran, Atlassian}}}{April 2021 -- Present}
      {PatientPoint $|$ AdTech} {Remote}
      \resumeItemListStart
        \resumeItem{Architect and engineer multi-tenant data pipelines from various sources (APIs, FTPs, Elastic Storage, Cloud Databases, Microservices, Streaming Services etc.) to a Snowflake data warehouse for data science, analysis and reporting.}
        \resumeItem \href{https://patientpoint.com/news/patientpoint_becomes_first_poc_publisher_to_earn_media_rating_council_accreditation/}{Technical lead on a multi-year initiative which secured multiple industry accreditations for data pipelines and reports, enabling incremental revenue in the hundreds of millions dollars.}
        % add href https://patientpoint.com/news/patientpoint_becomes_first_poc_publisher_to_earn_media_rating_council_accreditation/
        \resumeItem{Advise on Enterprise Architecture Review Board as an advocate the for data team on enterprise-spanning initiatives.}
        \resumeItem{Develop and implement data warehouse architectural standards including ETL/ELT, Datalake and Snowflake.}
        \resumeItem{Act as technical lead for projects spanning engineering, data modeling, data science,  and visualization disciplines.}
        \resumeItem{Delegate engineering work based on priority, skill set and business value to a multi-discipline team.}
        \resumeItem{Implemented CI/CD for Snowflake and Airflow via YAML and Github Actions.}
        \resumeItem{Lead post-merger tech stack transition from AWS+Redshift/Azure+Synapse to Snowflake, Airflow, and Fivetran.}
        \resumeItem{Actively contribute to agile and scrum ceremonies via backlog grooming, story writing and project planning.}
      \resumeItemListEnd
  
    \resumeSubheading
      {{Business Intelligence Developer} 
      $|$ \emph{\small\textmd{SQL Server, Azure, Python, PowerBI, Tableau}}}{January 2019 -- April 2021}
      {PatientPoint $|$ AdTech}{Cincinnati, OH}
      \resumeItemListStart
        \resumeItem{ Design, develop, and continuously improve fully automated reports and dashboards for consumption by multiple internal business units and external clients.}
        \resumeItem{Ensure report design and metric calculation adheres to industry standards in compliance auditors.}
        \resumeItem{Enable self-service reporting by gathering and documenting requirements then designing and deploying tailored, multi-use data models to specification. }
        \resumeItem{Act as a SME for reporting requests around user engagement data for a tablet product with appx. 60,000 units.}
        \resumeItem{Collaborate with external application development teams on user engagement logging specification and design.}
        \resumeItem{Participate in discussion and research for new and developing technologies to integrate into the current stack. }
        \resumeItem{Serve as a resource for Excel-primary teammates looking to expand their skill sets into SQL. }
      \resumeItemListEnd

    \resumeSubheading
      {IT Technician $|$ \emph{\small{\textmd{T-SQL, VB.net, PowerShell, Bash, Linux, Windows Server}}}}{March 2018 -- December 2018}
      {Melink Corporation $|$ Commercial Construction}{Milford, OH} 
      \resumeItemListStart
        \resumeItem{Develop, improve, and maintain a home-grown business intelligence application.}
        \resumeItem{Model historical data and market trends to predict business performance.}
        \resumeItem{Collaborate with management on continuous improvements aided by IT
infrastructure and applications.}
        \resumeItem{Perform research on purchasing recommendations for hardware and software.}
        \resumeItem{Maintain on-premise enterprise servers and end-user hardware.}
        \resumeItem{Monitor helpdesk ticket trends to develop proactive solutions.}
      \resumeItemListEnd
    \resumeSubheading
      {Sales Engineer Co-op} 
      %$|$ \emph{\small{\textmd{T-SQL, VB.net, Excel, PowerShell, Bash, Python}}}}
      {December 2014 -- March 2018}
      {Melink Corporation $|$ Commercial Construction}{Milford, OH}  
      
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Cincinnati, Lindner College of Business}{Cincinnati, OH}
      {Bachelor of Business Administration, Information Systems, Class of 2018}


  \resumeSubHeadingListEnd
  
%        \begin{itemize}[leftmargin=0.15in, label={}]
%         \small{\item{
%             \textbf{\\Coursework}{: Natural Language Processing, Optimization Models, Computer Vision, Data Mining, Neural Computation, Statistics, Product Design, Front and Back End Web Architecture} \\
%             }}
%         \end{itemize}
%
%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Databases}{: Snowflake, Postgres, Redshift, SQL Server, Oracle, Synapse, MySQL} \\
     \textbf{Languages}{: Various SQL dialects including SnowSQL and T-SQL, Python, JavaScript, C#, Java} \\
     \textbf{Technologies}{: Apache Airflow, Fivetran ETL, S3/Blob Storage, Git, GitHub CI/CD, Terraform, Kafka, Atlassian Tools} \\
     \textbf{Skills}{: Data Warehousing, Inmon/Kimball Data Modeling, ETL/ELT Design, IoT Data, Cloud Architecture, Agile, Scrum, Project Management, Requirements Gathering, Technical Writing & Doucmentation} \\

    }}
 \end{itemize}
%-----------Footer-----------
\iffalse
\begin{center}
    \textbf \tiny{References available upon request.} 
\end{center}
\fi

 %-----------PROJECTS-----------
\iffalse
\section{Projects and Publications}
    \resumeSubHeadingListStart
    \resumeProjectHeading
      {\href{https://www.ischool.berkeley.edu/projects/2022/tensorhero-ml}{\underline{\textbf{Tensor Hero}}} $|$ \emph{Python, PyTorch, librosa, SciPy}}{Sep. 2020 -- Present}
      \resumeItemListStart
        \resumeItem{Creating a machine learning system to produce playable Guitar Hero charts from any audio file.}
        \resumeItem{Managed a team of eight graduate students to deliver implemented system and user-facing website.}
        \resumeItem{Publishing a package of data science tools to allow an open source community to work with Guitar Hero data.}
      \resumeItemListEnd
      
     \resumeProjectHeading
      {\textbf{Soundr - A Therapy Matching Platform}}{Sep. 2021 -- May 2022}
      \resumeItemListStart
        \resumeItem{Founded a therapist-client matching startup through Berkeley's Lean Launchpad class, a selective early stage startup simulator led by Bay Area venture capitalists (via Berkeley Haas).}
        \resumeItem{Won the Peer Recognition Award by vote for being the most helpful individual consultant (out of 38 students) to other teams in the class via weekly peer-feedback forms.}
        \resumeItem{Interviewed over 120 therapists, clients, and industry experts to gain product-market fit.}
      \resumeItemListEnd
      
     \resumeProjectHeading
          {\href{https://github.com/elliottwaissbluth/DrumSynthesis}{\underline{\textbf{Drum Synthesis}}} $|$ \emph{Python, PyTorch, librosa}}{Feb. 2020 -- May 2020}
          \resumeItemListStart
            \resumeItem{Published in AI Music Creativity 2022 (link in heading).}
            \resumeItem{Created a variational autoencoder capable of producing a distribution of electronic drum samples.}
          \resumeItemListEnd
          
    \resumeProjectHeading
          {\href{https://github.com/elliottwaissbluth/Bayesian-Motion-Aftereffect}{\underline{\textbf{Bayesian Framework for Sensory Adaptation}}} $|$ \emph{Python, OpenCV}}{Oct. 2020 -- Dec. 2020}
          \resumeItemListStart
            \resumeItem{Proposed and implemented a computational framework to explain the motion aftereffect using Bayesian statistics.}
            \resumeItem{The framework synthesized several papers to account for multiple phenomena related to the motion aftereffect.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\fi


%
%-----------ACTIVITIES AND INTERESTS-----------
% \section{Activities and Interests}
%  \begin{itemize}[leftmargin=0.15in, label={}]
%     \small{\item{
%      \textbf{Snowboarding}{: Former president of The Ohio State Ski and Board Team. Freestyle instructor at Woodward Tahoe (Summer 2019).} \\
%      \textbf{Misc}{: Music, Climbing, Animation, Mountain Biking, Backpacking (Completed 165 mile solo hike July 2019).}
%     }}
%  \end{itemize}

\end{document}

% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------